\documentclass{article}


\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\titleformat{\section}
{\huge}
{}
{0em}
{\filcenter\bfseries}  [\titlerule]


\titleformat{\subsection}
{\bfseries\Large}
{$\bullet$}
{.25em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[---] 

\titlespacing{\subsection}
{0em}{.25em}{.25em}




\renewcommand{\maketitle}{

\begin{center}
	{\huge\bfseries
	\theauthor}
\vspace{.5em}


	\href{https://abhishrijoshi.com}{\underline{Persnol Website}} $|$ \href{https://in.linkedin.com/in/abhishri-joshi }{\underline {LinkedIn}} $|$ \href{mailto:abhishri@abhishrijoshi.com}{\underline {Email}} $|$ \href{https://github.com/abhishrijoshi}{\underline{GitHub}} $|$ +911234567891

\hfill \break
Address|Some place,Delhi,
DOB-19,Feb,2000


\end{center}
}







\begin{document}


\author{Abhishri Joshi}

\maketitle

\section{Technical Skills}


\subsection{Programming Languages }

C,C++,Haskell,Rust,Java,Solidity, Unix Scripting,COBOL,Swift

\subsection{Scripting Languages }
Python,Perl,Shell,R, Praat,Sed,Regex

\subsection{Markup Languages }
{\LaTeX}, HTML, CSS

\subsection{Can Speak}
English,Hindi, Marathi.

\subsection{Work Flow}
Vim,Tmux, For networked devices, ssh and either git,rsync or syncthing depending on the need.

\section{Project's}
\subsection{Custom Android}
An fork of Aosp with PixelOs goddies.

\subsection{Spotify Playlist downloader}
Download's Playlist's from spotify.

\subsection{Neumorphic Web library }
An Library written in css aiming to be usefull for neumorphism.

\subsection{Automated Instagram }
An automated instagram account.
Many more project's that you can find on git at \href{https://github.com/abhishrijoshi}{\underline{GitHub}}
 

\section{Additional}
Organized computer and English literacy workshops for underprivileged children in village's of India.
\hfill \break
I maintain a custom version of android and kernel for my device.

\section{Area of Interest}
Tinkering with micro computer's like raspberry pi, arduino. 
\hfill \break
Well versed with Tabla and Guitar.
\section{Education}
\subsection{Currently}
Studying Btech Computer Science in SRMIST Kattankulathur,Chennai.

\subsection{Completed} Class 12 and 10 in CBSE board.
\section{Job Experience}
\subsection{Part time }Freelancing in Computer science related project's since 2+ year's .

\end{document}
